---
title: "edld610_lab1"
author: "Cameron Kay"
date: "1/9/2019"
output: html_document
---

```{r setup, include=FALSE}
#load packages
library(rio)
library(here)
library(tidyverse)

#load data
df <- import(here("data", "rstats_tweets.rds")) %>%
  janitor::clean_names()
```

Some guidance: *You’ll want to count the number of times a screen name appears and select only the top 25*. 
  * First pull Commit 1, then reproduce the following figure.
  * You’ll want to count the number of times a screen name appears and select only the top 25.
  * Consider arranging in descending order, then using  dplyr::slice
  * Make the screen name a factor, ordered according to the number of times it appears.
  * Consider forcats::fct_reorder
  * coord_flip will be your friend here

```{r commit2}

df %>%
  count(screen_name) %>%
  arrange(desc(n)) %>%
  dplyr::slice(1:25) %>%
  mutate(screen_name = factor(screen_name)) %>%
  ggplot(aes(x = forcats::fct_reorder(screen_name, n), y = n)) +
    geom_col() +
    coord_flip()


```

